Hybrid platforms and bargaining power

### 2022-12-13 src/paper/application.tex
Add benchmark model equilibrium

\section{Model}

@@

@@

>>>>

\section{Model}
\label{sec:model}

@@

As shown in \textcite[]{anderson2021hybrid}, the utility functions described in section \ref{sec:model} give rise to a logit-type demand function.
Specifically, the demand for product $i$ of producer $T \in \{P, F\}$ is given by:
\begin{align*}
    x_{Ti} = \frac{\exp\left( \frac{v_T - p_{Ti}}{\mu} \right)}{A}
\end{align*}
where
\begin{align}
    A = \int_0^{N_F} \exp\left( \frac{v_F - p_{Fi}}{\mu} \right) \di + \int_0^{N_P} \exp\left( \frac{v_P - p_{Pi}}{\mu} \right) \di + 1.
    \label{eq:aggregate}
\end{align}
The producers' variable profit function is then given by
\begin{align}
    \pi^v_{Ti} = ( p_{Ti} - c_T ) \frac{\exp\left( \frac{v_T - p_{Ti}}{\mu} \right)}{A}.
    \label{eq:variable_profit}
\end{align}

Notice that, as each producer is infinitesimal, its pricing decision does not affect the aggregate $A$.
It follows that the profit maximizing price is a simple additive markup over marginal cost
\begin{align*}
    p^*_{Ti} = c_T + \mu,
\end{align*}
and the optimal profit is
\begin{align*}
    \pi^{v*}_{Ti} = \mu \frac{\exp \left( \frac{v_T - c_T - \mu}{\mu} \right)}{A}.
\end{align*}

For fringe firms, their total profit (including the investment cost $I_F$ and the entry fee $F_F$) is given by
\begin{align}
    \pi^{t*}_F = \mu \frac{\exp \left( \frac{v_F - c_F - \mu}{\mu} \right)}{A} - I_F - F_F.
    \label{eq:fringe_profit}
\end{align}

\subsection{Fringe entry}

Recall that there is an infinity of potential fringe entrants looking to enter the market.
Therefore, total profits in equilibrium must be zero.
Let us for the moment assume that fixed fees are low enough for some fringe firms to enter the market.
In this case, setting $\pi^{t*}_F$, equation \eqref{eq:fringe_profit} implies that the size of the aggregate is
\begin{align}
    A = \mu \frac{\exp \left( \frac{v_F - c_F - \mu}{\mu} \right)}{F_F + I_F}.
    \label{eq:aggregate_eq}
\end{align}
Substituting this into equation \eqref{eq:aggregate} and rearranging gives the number of fringe firms that enter the market:
\begin{align*}
    N_F = \frac{\mu}{F_F + I_F} - I_F N_P \exp \left( \frac{(v_P - v_F) - (v_F - c_F)}{\mu} \right) - \frac{1}{\exp \left( \frac{v_F - c_F - \mu}{\mu} \right)}.
\end{align*}

If, on the other hand, entry costs are too high, no fringe firms enter the market ($N_F = 0$).
In that case, the aggregate demand is just
\begin{align*}
    A = N_P \exp\left( \frac{v_P - c_P - \mu}{\mu} \right) + 1.
\end{align*}

@@

In the first period of the game, the platform chooses an entry fee to maximize its total profit, consisting of revenue from its own sales and the collected entry fees.
First, let us examine the case when the fees are low enough for the fringe to be feasible.
Profits from sales can be obtained by combining equations \eqref{eq:variable_profit} and \eqref{eq:aggregate_eq}:
\begin{align*}
    \pi_P^{v} = N_P (F_F + I_F) \exp \left( \frac{(v_P - v_F) - (c_P - c_F)}{\mu} \right).
\end{align*}
% TODO: other cases
It is increasing in the (1) number of the platform's products, (2) the platform's product advantage (larger market share) and (3) the entry costs for fringe firms (less competition).
The other component of the platform's profit, entry fees collected from the fringe, are given by
\begin{align*}
    \pi_P^{f} = N_F F_F = F_F \left[ \frac{\mu}{F_F + i} - N_P \exp \left( \frac{(v_P - v_F) - (v_F - c_F)}{\mu} \right) - \frac{1}{\exp \left( \frac{v_F - c_F - \mu}{\mu} \right)} \right].
\end{align*}

Combining these two, the platform's total profit as a function of the entry fee can be expressed as
\begin{align*}
    \pi_P^{t} = \mu\frac{F_F}{F_F + I_F} + N_P I_F \exp \left( \frac{(v_P - v_F) - (v_F - c_F)}{\mu} \right) - \frac{F_F}{\exp \left( \frac{v_F - c_F - \mu}{\mu} \right)}
\end{align*}

Now let us consider the case when the fringe is not present in the market.
In this case, the collected entry fees are obviously zero, and the platform's profit is simply given by
\begin{align*}
    \pi_P^{t} = \pi_P^{v} = \mu \frac{ N_P \exp \left( \frac{v_P - c_P - \mu}{\mu} \right)}{N_P \exp\left( \frac{v_P - c_P - \mu}{\mu} \right) + 1}.
\end{align*}

% Note that, although the platform's profit is increasing in the number of its products, the optimal entry fee does not depend on it.
% TODO: intuition
